### 2017-09-30 TF-vldb2018/sec-expt.tex

\etitle{Algorithms}. We implemented the following algorithms, all in C++:
(1) algorithm \optgrouprec for \teamF; (2) incremental algorithm \inc for \dynteamF;
(3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
(a) \mindia is to minimize the team diameter~\cite{Lappas09},
\revise{which is firstly proposed for the team formation problem;}
(b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
(c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
\revise{Most of the algorithms for \teamF, including  \mindia and \denalk, only compute the best team,}
while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
Based on this, we extend \mindia and \denalk to find top-$k$ teams in polynomial time.

@@

\revise{These verify that \optgrouprec can effectively preserve structural and capacity constraints for top-$k$ team formation \wrt edge and node satisfiability, and pertains a good team collaboration compatibility \wrt diameter and density.}

@@

\etitle{(i) Pattern updates}. We generated $5$ sets of hybrid pattern updates, varying the number of updates of each set from $1$ to $7$.
We tested the average time took by \inc to finish all these sets one by one.
The results are reported in Fig.~\ref{fig-exp-patinc-multi}.

Recall that \inc adopts a lazy update policy, which definitely affects the processing time of next updates.
However, we find \inc outperforms \optgrouprec \wrt average time, when the number of hybrid  pattern updates in each set is no more than (27\%, 31.5\%)  on (\citationd, \synthetic). This verifies the effectiveness of our lazy update policy.

\etitle{(ii) Data updates}. The setting is same as above. Varying the the amount of hybrid data updates in each set from 4\% to 24\%,
the results are reported in Fig.~\ref{fig-exp-datainc-multi}.
We find that \inc outperforms \optgrouprec when hybrid data updates are no more than (24\%, 28\%) on (\citationd, \synthetic).

\etitle{(iii) Simultaneous pattern and data updates}. Using the same setting and varying the simultaneous pattern and data updates $(\Delta P, \Delta G)$ from (4.5\%, 4\%) to (27\%, 24\%) in Fig.~\ref{fig-exp-hyb-datapat-multi},
We find that \inc outperforms \optgrouprec when updates in each set are no more than (18\%, 16\%) and (22.5\%, 20\%)
on \citationd and \synthetic, respectively.
%\looseness=-1

>>>>

\etitle{Algorithms}. We implemented the following algorithms, all in C++:
(1) algorithm \optgrouprec for \teamF; (2) incremental algorithm \inc for \dynteamF;
(3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
(a) \mindia is to minimize the team diameter~\cite{Lappas09}, which is firstly proposed for the team formation problem;
(b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
(c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
Most of the algorithms for \teamF, including  \mindia and \denalk, only compute the best team,
while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
Based on this, we extend \mindia and \denalk to find top-$k$ teams in polynomial time.

@@

These verify that \optgrouprec can effectively preserve structural and capacity constraints for top-$k$ team formation \wrt edge and node satisfiability, and pertains a good team collaboration compatibility \wrt diameter and density.

@@

\etitle{(i) Pattern updates}. We generated $5$ sets of hybrid pattern updates, varying the number of updates in each set from $1$ to $7$.
We tested the average time took by \inc to finish all these sets one by one.
The results are reported in Fig.~\ref{fig-exp-patinc-multi}.

Recall that \inc adopts a lazy update policy, which definitely affects the processing time of next updates.
However, we find \inc outperforms \optgrouprec \wrt average time, when the amount of hybrid  pattern updates in each set is no more than (27\%, 31.5\%)  on (\citationd, \synthetic). This verifies the effectiveness of our lazy update policy.

\etitle{(ii) Data updates}. The setting is same as above. Varying the amount of hybrid data updates in each set from 4\% to 28\%,
the results are reported in Fig.~\ref{fig-exp-datainc-multi}.
We find that \inc outperforms \optgrouprec when hybrid data updates are no more than (24\%, 28\%) on (\citationd, \synthetic).

\etitle{(iii) Simultaneous pattern and data updates}. Using the same setting and varying the simultaneous pattern and data updates $(\Delta P, \Delta G)$ from (4.5\%, 4\%) to (31.5\%, 28\%) in Fig.~\ref{fig-exp-hyb-datapat-multi},
We find that \inc outperforms \optgrouprec when updates in each set are no more than (18\%, 16\%) and (22.5\%, 20\%)
on \citationd and \synthetic, respectively.
%\looseness=-1
